---
title: "basic_visualization_in_r #1"
output: html_document
---
##reference: R graphics cookbook, Winston Chang 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This file will briefly cover the basic syntax of visualiztion

First, library, and our example data frame 

```{r cars}
library(tidyverse)

id=1:10
age=c(30,30,37,35,33,30,30,37,35,33)
gender=c("f","f","f","f","f","m","m","m","m","m")
weight=c(155,177,NA,144,199,180,199,166,168,176)
university=c("Duke","WFU","UNC","Duke","WFU","UNC","WFU","Duke","UNC","WFU")
height=c(80,34,56,34,98,80,34,56,34,98)
DF2=data.frame(id,age,gender,weight,university,height,stringsAsFactors = TRUE)
str(DF2)
DF2


```

## The basic 1

The basic bar graph syntax is as following:

ggplot(dataframe, aes(x= your x varialbe ))+
geom_bar()

we can start from this syntax. 

```{r}
ggplot(DF2, aes(x=id)) +
  geom_bar()


```
## further step 1

In the above example, we did not assigned y-axis. In this case, the default y is the number of the events that belongs to each x.
What about we want to assign x variable and y variable? 

in this case, you shoud assign your y value in aes(),
and in the geom_bar(stat="identity")

the default is geom_bar(stat="bin"). 
```{r}

ggplot(DF2, aes(x=id, y=height)) +
  geom_bar(stat="identity")

```

Let's say that you don't want the black color. 
in the geom_bar(), you can assign your color, and the outline color. 

fill=the color of the bar
color= the color of the outline. 

```{r}

ggplot(DF2, aes(x=id, y=height)) +
  geom_bar(stat="identity", fill="blue", color="green")

```

##further step 2

you want to present second variable, and want to tie the graph with this variable. 

than, in the ggplot(), you should add that variable using fill= argument. Dont' forget to add position="dodge" in the geom_bar()
```{r}

ggplot(DF2, aes(x=university, y=height, fill=gender)) +
  geom_bar(stat="identity",  position="dodge")

```

If you really want that green outline, you can always put that. 

```{r}

ggplot(DF2, aes(x=university, y=height, fill=gender)) +
  geom_bar(stat="identity",  position="dodge", color="green")

```

still don't like your graph color?

use scale_fill_brewer() or scale_fill_manual()

```{r}


ggplot(DF2, aes(x=university, y=height, fill=gender)) +
  geom_bar(stat="identity",  position="dodge", colour="green") +
  scale_fill_brewer(palette="Pastel3")

# looks good? 
  

```

```{r}


ggplot(DF2, aes(x=university, y=height, fill=gender)) +
  geom_bar(stat="identity", color="black", size=0.4) # you can assign the outline size. 


```
you can also remove that guide. 
````{r}




ggplot(DF2, aes(x=university, y=height, fill=gender)) +
  geom_bar(stat="identity", color="black", size=0.4) +
  scale_fill_brewer(palette="pastel3", guide=FALSE)


```

## label in the bar graph? 

```{r}

ggplot(DF2, aes(x=university, y=height, fill=gender)) +
  geom_bar(stat="identity",  position="dodge") +
  geom_text(aes(label=height))
```